From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-08-21 WOLFHPC15/article/ms_msc.tex
Big Fig 3 splits into 2.

%----------------------------------------
\subsection{Multi Stencil Language}
%----------------------------------------

@@

\begin{figure*}[t]
\subfloat[\label{fig:grammar}]
{\lstinputlisting[basicstyle=\small,mathescape,frame=single,language=Python,numbers=left,linewidth=0.45\textwidth]{grammar.txt}}
%\hfill
\hspace{1.5cm}
\subfloat[\label{fig:mslex}]
{\lstinputlisting[basicstyle=\small,mathescape,frame=single,language=Python,numbers=left,linewidth=0.45\textwidth]{example.txt}}
\caption{(a) Grammar of the Multi-Stencil Language, (b) Example of a MSL program}
\end{figure*}

As mentioned in the previous section, the Multi Stencil Language (MSL) is an agnostic descriptive language for multi-stencil simulations. Six main sections are required in a MSL description that match the six elements of the formal definition; they describe: \textbf{1.}\,the mesh, \textbf{2.}\,the mesh entities, \textbf{3.}\,the computation domains with their inter-dependencies, \textbf{4.}\,the data, \textbf{5.}\,the time iterations, and finally \textbf{6.} the computations.
Figure~\ref{fig:grammar} shows the grammar of MSL. Lines 1 to 9 define what is a MSL program with the different parts mentioned above. The remaining of this section describes these different parts of a MSL program and presents an example.
One can notice that terminals are the string identifiers \texttt{meshid}, \texttt{meshdom}, \texttt{compdomid}, \texttt{dataid}, \texttt{compid} and \texttt{neighborid}. The terminal \texttt{num} is an integer terminal.

\subsubsection*{Mesh and Mesh Entities}
As illustrated in the first line of the grammar in Figure~\ref{fig:grammar}, a mesh is simply defined by a string identifier.
The different kind of mesh entities are described as a list of identifiers (lines 2, 10 and 11 in Figure~\ref{fig:grammar}).
Figure~\ref{fig:mslex} presents an example of a mesh named \texttt{cart} used to represent a Cartesian mesh, and three kind of mesh entities: \texttt{cell}, \texttt{edgex}, and \texttt{edgey}.

>>>>

@@

\begin{figure}[t]
  \hspace{5mm}
  \begin{minipage}[t]{.49\textwidth}
    %  \subfloat[\label{fig:grammar}]
    {\lstinputlisting[basicstyle=\small,mathescape,frame=single,language=Python,numbers=left,linewidth=.87\textwidth]{grammar.txt}}   
    \caption{Grammar of the Multi-Stencil Language. \label{fig:grammar}}
  \end{minipage}
\end{figure}

\begin{figure}[t]
\hspace{5mm}
  \begin{minipage}[t]{.49\textwidth}
    %\subfloat[\label{fig:mslex}]
    {\lstinputlisting[basicstyle=\small,mathescape,frame=single,language=Python,numbers=left,linewidth=0.87\textwidth]{example.txt}}
    \caption{Example of a MSL program. \label{fig:mslex}}
      \end{minipage}
\end{figure}

%----------------------------------------
\section{Language and Parallelization}
\label{sect:msmsc}
%----------------------------------------
\subsection{Multi Stencil Language}
%----------------------------------------

As mentioned in the previous section, the Multi Stencil Language (MSL) is an agnostic descriptive language for multi-stencil simulations. Six main sections are required in a MSL description that match the six elements of the formal definition; they describe: \textbf{1)}\,the mesh, \textbf{2)}\,the mesh entities, \textbf{3)}\,the computation domains with their inter-dependencies, \textbf{4)}\,the data, \textbf{5)}\,the time iterations, and finally \textbf{6)} the computations.
Figure~\ref{fig:grammar} shows the grammar of MSL. Lines 1 to 9 define what is a MSL program with the different parts mentioned above. The remaining of this section describes these different parts of a MSL program and presents an example.
One can notice that terminals are the string identifiers \texttt{meshid}, \texttt{meshdom}, \texttt{compdomid}, \texttt{dataid}, \texttt{compid} and \texttt{neighborid}. The terminal \texttt{num} is an integer terminal.

\subsubsection*{Mesh and Mesh Entities}
As illustrated in the first line of the grammar in Figure~\ref{fig:grammar}, a mesh is simply defined by a string identifier.
The different kind of mesh entities are described as a list of identifiers (Lines 2, 10 and 11 in Figure~\ref{fig:grammar}).
Figure~\ref{fig:mslex} gives an example of a mesh named \texttt{cart} used to represent a Cartesian mesh, and three kinds of mesh entities: \texttt{cell}, \texttt{edgex}, and \texttt{edgey}.
